\section{X}%
\label{sec:X}

\begin{frame}
  \frametitle{Problem I: I Want Candy!}
  \begin{itemize}
    \item No official participants solved :( but congratulations to former student \textbf{one man retirement home} (Chris Rech) for solving!
    \item At first glance, the problem might look familiar. Remember the knapsack problem?
    \item Let's ignore the special deals for now. We are left with a bunch of candies with happiness values and their prices. Let's find out what is the best deal we can get with $d$ money (this is just classic knapsack)
    \item Let $dp[i][j]$ be the biggest happiness value we can get after we have examined the first $i$ candies and used $j$ dollars
      \[ dp[i][j] = \max \begin{cases} dp[i-1][j-p[i]] + h[i], & \text{(buy the $i$-th candy)}\\ dp[i-1][j], & \text{(don't buy the $i$-th candy)} \end{cases}\]
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Problem I: I Want Candy! (continued)}
   \begin{itemize}
    \item Now, let's take into account the special deals. Let's look at the following case:\\
        happiness: 5 7 9 1 2\\
        price: 8 3 2 10 1\\
        brand: 1 1 2 2 2\\
        brand price: 7 11\\
    \item If we sneak the special deals into the candy arrays like this:\\
        $[candy|brand]$ happiness: 5 7 \textbf{12} 9 1 2 \textbf{12}\\
        $[candy|brand]$ price: 8 3 \textbf{7} 2 10 1 \textbf{11}\\
        $[candy|brand]$ brand: 1 1 \textbf{1} 2 2 2 \textbf{2}\\
    \item Here, we can almost apply the knapsack DP. Only 1 constraint left that we need to take care of. That is:
    \begin{itemize}
        \item If we buy a candy of a brand, we can't pay the special price to buy all candies of that brand. 
        \item If we pay the special price to buy all candies of a brand, we can't buy any individual candy in that brand.
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Problem I: I Want Candy! (cont.)}
  \begin{itemize}
    \item Let's modify the first case of our dp:
      \[dp[i][j] = dp[\boldsymbol{i-1}][j-p[i]] + h[i], \text{(buy the $i$-th $[candy|brand]$)}\]
    \item to:
      \[dp[i][j] = dp[\boldsymbol{i-k[i]}][j-p[i]] + h[i], \text{(buy the $i$-th $[candy|brand]$)}\]
    where $i-k[i]$ is the maximum $j<i$ s.t. the $j$-th $[candy|brand]$ can be bought together with the $i$-th $[candy|brand]$. So
    \[ k[i] = \begin{cases}
      \text{\# of candies of brand $i$}, & \text{if a brand}\\
      1, & \text{if a candy}
    \end{cases}
      \]
    \item With this, the constraint discussed in the previous slide is taken care of!
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Problem I: I Want Candy! (cont.)}
  \begin{itemize}
    \item \textbf{The tricky part} of this problem is to place the brands and candies into an order that we can perform knapsack-like DP 
    \item Another ``not-necessarily-hard'' part of this problem is that it helps to have heard of the classic knapsack problem
    \item Although the idea is straightforward, coding up the part ``sneak the brands into candy arrays'' might be a bit annoying
    \item Since the problem wasn't solved, we will leave it to you to code! :)
  \end{itemize}
\end{frame}
